\chapter*{Acknowledgments}
\label{ch:Acknowledgments}
\markboth{Acknowledgments}{}
\addcontentsline{toc}{chapter}{Acknowledgments}

Many people have contributed towards the outputs of this thesis.
I would sincerely like to acknowledge their contributions here.

I would like to express my gratitude to Prof.~Michel~Orrit for patiently guiding me through all the stages of my PhD.
Thanks for giving new insights and directions to the project.
His wide knowledge and passion for science has been very inspiring.
I would also like to express my gratitude to Prof.~Gerard~Canters for his kind supervision and guidance.
Thanks for sharing your academic and non-academic experiences which made me believe the exciting life a researcher can have.
I would like to thank Prof.~Thijs~Aartsma for many scientific discussions and assistance with the optical microscope.

I am thankful to Dr.~Martin Caldarola for many scientific collaborations during PhD.
His simulations and calculations contributed largely to the chapter-4 of this thesis.
Discussions with him both in the lab and in the tennis court were insightful.
I would like to thank Dr.~Ankur Gupta and Dr.~Saumyakanti Khatua for getting me started with the PhD.
I am indebted to Dr.~Xueyan Miao for her assistance in experiments which contributed to Chapter-4 and 5 of this thesis.
I would like to thank Sebastiaan van Mulken for his contribution to the chapter on azurin and for long discussions on both scientific and non-scientific topics.
Thanks to Aron Kamp and Mudit Garg for their dedication towards the bachelor projects.
I would like also to thank Dr.~Siddharth Ghosh for collaborations and fruitful discussions.
A big thanks to Weichun Zhang for day-to-day discussions in the lab and for being a good friend. 

I gratefully acknowledge Henriette van Leeuwen and Yvonne Kerkhof for the administrative supports, Harmen van der Meer for making the flow cells and several components of the microscope, and Peter van Veldhuizen for fixing the electronics.
I would like to thank Ing. Lionel Ndamba for helping me with protein synthesis and purifications and Marcel Winter for gracefully providing mutants of azurin. 

I am grateful to Dr.~Saptaswa Sen for teaching me the labeling of azurin and demonstrating lab tools.
I was fortunate to share my office with Dr.~Marija Mucibabic. Her optimism and positive approach towards scientific/non-scientific problems was inspiring and energizing.
I am thankful to Dr.~Pravin Kumar for assistance with the preparation of lipid vesicles and for discussions on various topics.
I gratefully acknowledge Kirsten Martens for dutch translation of the summary.
I am thankful to my paranymphs and good friends Thomas Jollans and Dr. Martin Baaske.
I am also thankful to everyone who created a friendly and scientific environment in Leiden: Lei, Enrico, Kamran, Subhasis, Pedro, Nico, Aquiles, Amin, Xuxing, Zoran, Patrick, Ben, Gabriele, Faezh, Donny, Dirk, Sumit, Casper, Vera, Artur, Neli, Redmar, Wim, Sara, Veer, Karthick.

Finally, I would like to thank my grandparents for their endless love, encouragements and for giving me my best memories.